Supplemental Materials for: Meta-analytic approaches and effect sizes to account for ‘nuisance heterogeneity’ in comparative physiology

### 2021-10-04 supp.Rmd
Added the details of searches to supplement. Moved from main MS

### Details on Study Selection
Here we provide greater detail on the search strategy, keyword selection and the numbers of final studies included at each step pf the screening process for our survey. Figure \@ref(fig:figS1) outlines our PRSIMA flowchart detailing the number of papers hit, their sources and how many records were excluded and included at each screening phase. The full search strings used to refine our search query can be found in Table \@ref(tab:tabS1). Note that results from our final searches (25 & 28) are the ones we used. Our query was restricted to a pre-specified set of comparative physiology journals within the last 6 years of publication. The journals used and their ISSN numbers are provided in Table \@ref(tab:tabS2). In total, out of the 79 papers screened at the full-text stage we ended up including 62 full texts. We excluded N = 17 meta-/comparative analyses because they: 1) did not include physiological traits (N = 4); 2) were empirical studies that collected their own data and did not collate data from the literature (N = 10); 3) Were not actual quantitative syntheses, but rather systematic reviews (N = 1) and 4) were studies with a focus on biomechanics (N = 2).

>>>>

### Details on Study Selection
Here we provide greater detail on the search strategy, keyword selection and the numbers of final studies included at each step of the screening process for our survey. We searched for studies that included: ‘meta-analysis,’ ‘meta regression’ , ‘comparative analysis,’ ‘comprehensive analysis’ ‘global analysis’ or ‘macro physiology’ in their title or abstract, restricting our search to key comparative physiology journals (detailed in Table S1 and S2 - Supplementary Materials) within the last 6 years. The journals used and their ISSN numbers are provided in Table \@ref(tab:tabS2). The full search strings used to refine our search query can be found in Table \@ref(tab:tabS1). Initial searches were conducted in Scopus between May 16 and 18, 2021. We updated our survey with an additional search on September 1, 2021 with the addition of new journals (See Table \@ref(tab:tabS1) and \@ref(tab:tabS2)).  We expected this to provide a contemporary overview of quantitative syntheses in comparative physiology while making the survey and screening feasible. Note that results from our final searches are the ones we used.

All title, abstract and full text screening was done by two people (DWAN and ML). Any disagreements were resolved by discussion to reach a consensus. Out of the 417 papers originally identified, 79 full texts were screened for eligibility, and we included a total of 62 for final data extraction. We excluded N = 17 meta-/comparative analyses because they: 1) did not include physiological traits (N = 4); 2) were empirical studies that collected their own data and did not collate data from the literature (N = 10); 3) Were not actual quantitative syntheses, but rather systematic reviews (N = 1) and 4) were studies with a focus on biomechanics (N = 2). Figure \@ref(fig:figS1) outlines our PRSIMA flowchart detailing the number of papers hit, their sources and how many records were excluded and included at each screening phase.

We included comparative studies / meta-analyses that were focused on physiological questions. Narrative reviews and comments were not considered because they did not collate quantitative data from the literature. Studies needed to have collected physiological trait data, such as hormone levels, thermal physiological parameters (Critical thermal maximum (CTmax), critical thermal minimum (CTmin), thermal preferences, thermal breadth, lethal thermal tolerance limit (LT50), lethal thresholds), metabolic rates (routine, maximum, and minimum metabolic rate, aerobic scope), enzyme reaction rates and concentrations, oxidative stress measures and consequences (e.g., DNA damage, teleomere attrition), performance (e.g., maximum heart rates, sprint speed, swim speed) and growth rates, body composition (e.g., fatty acid profiles) and immune traits (e.g., cell function, antibodies). Studies were also included if they measured the relationship between physiological traits and body size (e.g., metabolic scaling), reproductive allocation, or survival across taxa. Studies on behavior were only included if the synthesis was explicitly interested in the proximate physiological drivers of behavioral variation. We also included meta-analyses that quantified the change in physiological traits in response to environmental variation (i.e., phenotypic plasticity). While many studies in comparative physiology collect data as part of a comparative analysis, we focus here only on studies collating data from existing literature because this is the major data source in quantitative syntheses. We excluded quantitative syntheses interested in phenology, biomechanics, sexual size dimorphism (i.e., except if the study was interested in sexual differences in physiological traits), those focused on validating physiological methodology, or characterising population genetic structure, gene transcription, and quantitative genetics. There were also meta-analyses that focused on colour evolution which varied in their goals but were most often not focused on physiological questions. As such, these studies were also excluded. We restricted our focus to animal studies because most plant synthesis papers were focused on ecological (e.g., quantified changes in abundance and distribution of species) or agricultural questions (e.g., studies on soil microbial function, nitrogen and phosphorus capture, methane output, and greenhouse gas emissions).
